% Revision 3.08 - Maintained by Arash Abadpour
%
\section{Employment History}
%
\cventry{2016--Current}{Senior Scientific Developer}{Fio Corporation, Toronto, Canada}{}{}{Utilization of Machine Learning algorithm for the purpose of visual identification and analysis of Rapid Diagnostics Tests (RDT) for infectious diseases such as HIV, Malaria, Dengue, and others.}
%
\cventry{2015--2016}{Research Scientist}{Intellijoint Surgical, Waterloo, Canada}{}{}{Research on surgery-assistance products which utilize machine vision in order to carry out and confirm geometrical measurements.}
%
\cventry{2009--2015}{Researcher}{Imaging Group, Epson Canada Limited, Toronto, Canada}{}{}{Conduct research and recommend solutions for problems in the fields of Visual Inspection, Symbology Detection, 3D Object Detection and Pose Estimation, Camera Calibration, Augmented and Virtual Reality, 3D Scan/Display Systems.}
%
\cventry{2001--2004}{Process Control Engineer}{Karband Eng. Co., Tehran, Iran}{}{}{Responsible for design, implementation and erection of PLC-based control systems for medium-sized machinery in pipe and profile production plants.}
%
\cventry{1998--2009}{Research Assistant}{University of Manitoba, Telecommunications Research Laboratories (TRLabs) Winnipeg and Biomechanics Laboratory, Sharif University of Technology}{}{}{Conduct research on projects related to Network Optimization, Earthquake Damage Detection using Satellite Imagery, Human Gait Analysis, 3D Surface Reconstruction, Color Image Processing with Applications in Watermarking, Encryption, Compression, Color Transfer, Grayscale Image Colorization, and Pornography Detection.}
%
\cventry{2005}{University Instructor}{Shariati University}{}{}{Digital Image Processing (Undergraduate Course).}
%
\cventry{2004--2007}{Teaching Assistant}{University of Manitoba and Sharif University of Technology}{}{}{For Advanced Digital Image Processing (Graduate Course), Digital Control, and Communication Systems (Undergraduate Courses).}
%