\section{Industry Experience}

\cventry{}{Machine Learning}{\newline
$\circ$ Classifier design, training, evaluation, and productization.\newline
$\circ$ Neural Network training and deployment, including Deep Learning and Convolutional Neural Networks.\newline
$\circ$ Ground-truth data collection and tagging as the back-end for training and evaluation of ML utilizing AWS/GCS.\newline
$\circ$ Offline ML training orchestration on a cluster of loosely--connected machines.\newline
$\circ$ Traceability management for data and models in order to satisfy regulatory requirements.\newline
$\circ$ On-the-device deployment of ML algorithms, given processing power, execution time, and battery consumption requirements.\newline
$\circ$ User interface design for ML algorithms, for the purposes of data tagging, problem specification, and assessment of the results.\newline
$\circ$ Deployment management, including model transfer to the production pipeline}{}{}{} 

\cventry{}{Image Processing}{\newline
$\circ$ General image processing, including grayscale, color, infrared, and depth image processing.\newline
$\circ$ Semantic Segmentation of aerial images using Convolutional Networks for insurance and real estate purposes.\newline
$\circ$ Image processing for robotics applications, including pose estimation, camera calibration, and stereo processing.\newline
$\circ$ Bilateral and trilateral filtering for the purposes of noise removal and interpolation}{}{}{} 

\cventry{}{Machine Vision}{\newline 
$\circ$ 3D object detection using mono and stereo camera systems.\newline 
$\circ$ 3D object pose estimation using low and high level features and training data collected on real or CAD data.\newline 
$\circ$ Bin picking using a robotic arm.\newline 
$\circ$ Visual inspection of output of printing processes as well as fidelity of manufactured parts}{}{}{} 

\cventry{}{Photogrammetry}{\newline
$\circ$ Fiducial-based pose estimation, including utilizing available technologies such as ARToolKit and ARTag, as well as designing in-house solutions.\newline
$\circ$ NIR-domain tracking for the purpose of sub-millimeter and sub-degree 6 DoF pose estimation}{}{}{}

\cventry{}{Medical Image Processing}{\newline 
$\circ$ DICOM import and processing.\newline
$\circ$ Geometric modeling of organs using MRI slices.\newline
$\circ$ Sterile-field image processing for the purpose of surgical navigation}{}{}{} 

\cventry{}{Optimization}{\newline 
$\circ$ Inverse problem-based parameter estimation using least mean square and Levenberg-Marquardt minimization.\newline 
$\circ$ Stochastic optimization in the presence of outliers using RANSAC and robustified cost minimization.\newline 
$\circ$ Fuzzy modeling of multi-layer systems, especially within the field of pattern recognition, using Bayesian models}{}{}{} 

\cventry{}{Range-Data Processing}{\newline 
$\circ$ Data acquisition and calibration of depth sensors, including stereo, structured light and Time of Flight (ToF) sensors.\newline 
$\circ$ RGBD filtering using bilateral and trilateral filtering pipelines.\newline 
$\circ$ Depth fusion between multiple depth sources as well as between a depth source and a raster image sensor.\newline
$\circ$ Multi-sensor depth registration utilizing both 3D and 2D features and different variations of the Iterative Closest Point (ICP) algorithm.\newline
$\circ$ Depth up-sampling and noise-reduction}{}{}{} 

\cventry{}{Human-Machine Interface}{\newline 
$\circ$ Data acquisition and calibration of augmented and virtual reality systems.\newline 
$\circ$ 3D scan/display systems utilizing multiple depth sensors}{}{}{}

\cventry{}{Pattern Recognition}{\newline 
$\circ$ Cost function derivation using Bayesian Inference for the purpose of clustering and modeling.\newline 
$\circ$ Unsupervised clustering using FCM, PCM, FPCM, and other variants.\newline 
$\circ$ Extensive research on the stability of fuzzy clustering models.\newline 
$\circ$ Principal Component Analysis (PCA) for color classification, including skin detection and color image segmentation}{}{}{} 

\cventry{}{Symbology}{\newline 
$\circ$ Symbology detection and interpretation, using available technologies as well as designing in-house solutions}{}{}{} 

\cventry{}{Computational Photography}{\newline 
$\circ$ Color transfer between color images and color video sequences.\newline 
$\circ$ Colorization of available grayscale image and video sequences using other color content}{}{}{}

\cventry{}{Image Data Management}{\newline
$\circ$ Visual watermarking and data hiding using redundancy in the spectral domain}{}{}{} 

\cventry{}{Inertial Data Processing}{\newline
$\circ$ Accelerometer data processing for the purpose of validation and augmentation of optical systems}{}{}{} 

