\section{Publications}

\subsection{Refereed Journal Papers}

\cvline{}{\textbf{Arash Abadpour} ``\emph{Rederivation of the Fuzzy-Possibilistic Clustering Objective Function through Bayesian Inference}'', Fuzzy Sets and Systems, Accepted for Publication, October 2015}% Connie

\cvline{}{\textbf{Arash Abadpour} ``\emph{Incorporating spatial context into fuzzy-possibilistic clustering using Bayesian inference}'', Journal of Intelligent and Fuzzy Systems, Accepted for Publication, August 2015}% Calista

\cvline{}{\textbf{Arash Abadpour} ``\emph{A Sequential Bayesian Alternative to the Classical Parallel Fuzzy Clustering Model}'', Information Sciences, Volume 318, October 2015, Pages 28--47}% Belinda

\cvline{}{\textbf{Arash Abadpour} ``\emph{On Applications of Pyramid Doubly Joint Bilateral Filtering in Dense Disparity Propagation}'', 3D Research, Volume 5, Issue 2, 25 April 2014, Pages 1--20.}% Margo

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Anthony C.K. Soong, ``\emph{Approximation Algorithms For Maximizing The Information-Theoretic Sum Capacity of Reverse Link CDMA Systems}'', AEU - International Journal of Electronics and Communications, Volume 63, Issue 2, 4 February 2009, Pages 108--115.}%W247 

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei. ``\emph{A Novel Color Image Compression Method using Eigenimages}'', Journal of Iranian Association of Electrical and Electronics Engineers - Volume 5, No.2, Fall and Winter 2008, Pages 45--53.}%W24    

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei. ``\emph{Color PCA Eigenimages and Their Application to Compression and Watermarking}'', IEE Image \& Vision Computing, Volume 26, Issue 7, July 2008, Pages 878--890.}%W24

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei ``\emph{Principal Color and Its Application to Color Image Segmentation}'', Scientia Iranica - Volume 15, No. 2, April 2008, Pages 238-245.}%W178

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Anthony C.K. Soong, ``\emph{Closed Form Solution for Maximizing the Sum Capacity of Reverse-Link CDMA System with Rate Constraints}'', IEEE Transactions on Wireless Communications, Volume 7, Issue 4, April 2008, Pages:1179--1183.}%W210J1

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Jeff Diamond, ``\emph{Video-on-Demand Network Design And Maintenance Using Fuzzy Optimization}'', IEEE Transactions on Systems, Man, and Cybernetics, Part B, April 2008, Volume 38, Issue 2, Pages: 404--420.}%W261SMC, fVoDSMC

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, ``\emph{Approximate algorithms for maximizing the capacity of the reverse link in multiple-class CDMA systems}'', in Operations Research and Cyber-Infrastructure, M. J. Saltzman, J. W. Chinneck, and B. Kristjansson, Eds. Springer, 2008, Pages: 237--252}%W286

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{An Efficient PCA-based Color Transfer}'', Visual Communication \& Image Representation, February 2007, Volume 18, Number 1, Pages, 15--34.}%W47

\cvline{}{\textbf{Arash Abadpour}, Shohreh Kasaei, S. Mohsen Amiri, ``\emph{Fast Registration of Remotely-Sensed Images for Earthquake Damage Estimation}'',  EURASIP Journal on Applied Signal Processing, Volume 2006 (2006), Article ID 76462.}%W75, http://www.hindawi.com/GetArticle.aspx?doi=10.1155/ASP/2006/76462, 

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei. ``\emph{Unsupervised, Fast and Efficient Color Image Copy Protection}'',  IEE Proceedings Communications, October 2005, Volume 152, Issue 5, Pages 605--616.}%W49

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei ``\emph{Pixel-based Skin Detection for Pornography Filtering}'', Iranian Journal of Electrical and Electronic Engineering (IJEEE), July 2005, Volume 1, No. 3, Pages 21--41.}

\subsection{Refereed Conference Papers}

\cvline{}{\textbf{Arash Abadpour} and Attahiru Sule Alfa, ``\emph{Approximate Algorithms for Maximizing the Capacity of the Reverse Link in Multiple-Class CDMA System}'', Accepted in 11th INFORMS Computing Society Conference, Charleston 2009 (ICS'09).}%W286ICS'09

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Jeff Diamond, ``\emph{Fuzzy Design of A Video-on-Demand Network}'', Accepted in 7th IEEE International Symposium on Signal Processing and Information Technology (ISSPIT 2007).}%W261ISSPIT07

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Anthony C.K. Soong, ``\emph{A More Realistic Approach to Information-Theoretic Sum Capacity of Reverse Link CDMA Systems in a Single Cell}'', In the IEEE International Conference on Communications (ICC 2007), Glasgow, Scotland.}%W210

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Anthony C.K. Soong, ``\emph{Capacity-Share Controlled Information-Theoretic Sum Capacity of Reverse Link Single-Cell CDMA Systems}'', In the 2007 IEEE 65th Vehicular Technology Conference, (VTC2007 Spring), Dublin, Ireland.}%W242 

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Anthony C.K. Soong, ``\emph{Information-Theoretic Sum Capacity of Reverse Link CDMA Systems in A Single Cell, An Optimization Perspective}'', In the 8th Annual Conference for Canadian Queueing Theorists and Practitioners, CanQueue 2006, Banff, Calgary, Canada.}%W210

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Anthony C.K. Soong, ``\emph{Closed Form Solution for QoS-Constrained Information-Theoretic Sum Capacity of Reverse Link CDMA Systems}'', In the 2nd ACM Q2SWinet 2006, Torremolinos, Malaga, Spain.}%W210

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{Multi.Layer Representation of Grayscale Images and Its Generalization}'', In the 14th  Iranian Conference on Electrical Engineering (ICEE2006), Iran.}%W164

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{Deliberate distortion of color image and video resources for copyright protection}'', In the 5th IEEE International Symposium on Signal Processing and Information Technology (ISSPIT 2005), Athens, Greece, pages 369--374, 2005.}%W142

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{Comprehensive Evaluation of the Pixel-Based Skin Detection Approach for Pornography Filtering in the Internet Resources}'', In the International Symposium on Telecommunications, (IST 2005), Pages 829--834, Shiraz, Iran, September 2005.}%W157

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{Wavelet-PCA-Based Compression Method for Color Images (Invited Paper)}'', In the First Symposium on Wavelet and its Applications, Tehran, Iran, February 2005.}%W24

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{An Unsupervised Fast Color Transfer Method}'', In the 13th  Iranian Conference on Electrical Engineering (ICEE2005), Zanjan, Iran, 2005.}%W51

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{A New Fast Robust Color Image Watermarking Method using FPCA Clustering}'', In the 10th Annual CSI Computer Conference (CSICC2005), Pages 246--251, Tehran, Iran, February 2005.}%W35

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{Fast Registration of Remotely Sensed Images}'', In the 10th Annual CSI Computer Conference (CSICC2005), Pages  61--67, Tehran, Iran, February 2005.}%W12

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{New Tree Decomposition Method for Color Images}''. In the  10th Annual CSI Computer Conference (CSICC2005), Pages 48--52, Tehran, Iran, February 2005.}%W24

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{A New Fast Fuzzy Method for Query Region Extraction from Color Images}''. In the 10th Annual CSI Computer Conference (CSICC2005), Pages 53--59, Tehran, Iran, February 2005.}%W37

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{Novel Color Image Compression Method using Eigenimages}'', In the third Conference on Machine Vision, Image Processing \& Applications, (MVIP2005), volume 1, Pages 340--346, Tehran, Iran, Februrary 2005.}%W24

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{Novel Method for Unsupervised Fuzzy Change Detection in Multispectral Remotely Sensed Images}'', In the third Conference on Machine Vision, Image Processing \& Applications, (MVIP2005), Volume 1, Pages 270--277, Tehran, Iran, February 2005.}%W12

\cvline{}{\textbf{Arash Abadpour}, S. Bagheri S, and Shohreh Kasaei, ``\emph{A New Method for Agent-based Color Clustering}'', In the World Congress on Fuzzy Logic, Soft Computing and Computational Intelligence Theories and Applications (IFSA2005), Beijing, China, July 2005.}%W26

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{A New FPCA-Based Fast Segmentation Method for Color Images}'', In the 4th IEEE International Symposium on Signal Processing and Information Technology (ISSPIT 2004), Pages 72--75, Rome, Italy, December 2004.}%W27

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{A Fast and Efficient Fuzzy Color Transfer Method}'', In the 4th IEEE International Symposium on Signal Processing and Information Technology (ISSPIT 2004), Pages 491--494, Rome, Italy, December 2004.}%W4

\cvline{}{Roya Narimani, Maryam HoviatTalab, \textbf{Arash Abadpour}, and Azadeh Yadollahi. ``\emph{Vibration Measurement And Analysis Using Image Processing Method}'',  In the proceedings of the 7th Biennial Conference on Engineering Systems Design and Analysis, (ESDA), Manchester, UK, July 19--22, 2004.}%W9

\cvline{}{Maryam HoviatTalab, Roya Narimani, Azadeh Yadollahi, and \textbf{Arash Abadpour}, ``\emph{New Image-based System for Vibration Measurement, Specially Developed for Forced Human Vibration Analysis}'', In the ASME International Mechanical Engineering Congress and RD\&D Expo, (IMECE2004), Anaheim, California, November 13--19, 2004.}%W9

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{A New PCA-Based Robust Color Image Watermarking Method}'', In the 2nd IEEE Conference on Advancing Technology in the GCC: Challenges, and  Solutions (IEEE-GCC 2004), Pages 326--331, Manama, Kingdom of Bahrain, November 2004.}%W24

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{A New Principle Component Analysis Based Colorizing   Method}'', In the 12th  Iranian Conference on Electrical Engineering (ICEE2004), Mashhad, Iran, May 2004.}%W3

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{New PCA-based Compression Method for Natural Color Images}''. In International Workshop on Computer Vision, IPM, Tehran, Iran, April 2004.}%W5

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{Performance Analysis of Three Likelihood Measures for Color Image Processing}''. In International Workshop on Computer Vision, IPM, Tehran, Iran, April 2004.}%W18

\cvline{}{\textbf{Arash Abadpour} and Shohreh Kasaei, ``\emph{A New Parametric Linear Adaptive Color Space and its PCA-based Implementation}''. In The 9th Annual CSI Computer Conference (CSICC2004), Volume 2, Pages 125-132, Tehran, Iran, February 2004.}%W1

\cvline{}{F. Malekipour, \textbf{Arash Abadpour}, Farzam Farahmand, R. Narimany, ``\emph{Study of Effect of Number and Location of the Control Points on the Accuracy of 3D Reconstruction of Coordinates in Gait Analysis Systems}'', In the 11th Iranian Annual Biomechanics Conference, Tehran, Iran, February, 2003 (Persian).}%W?

\cvline{}{F. Malekipour, \textbf{Arash Abadpour}, Farzam Farahmand, R. Narimany, ``\emph{Performance Analysis of the Direct Linear Transform for Marker Reconstruction in Motion Analysis Applications}'', In the First Seminar on Biomechanics and Human Motion Analysis, Imam Hospital, Tehran, Iran, November 2002 (Persian).}%W?

\cvline{}{\textbf{Arash Abadpour}, Azadeh Yadollahi, ``\emph{Developing a Software Platform to Use Anaglyph Glasses for 3D Visualization}'', National Computer Conference (NCC2003), Mashhad, Iran, 2003 (Persian).}%W?

\cvline{}{Roya Narimani, Farzam Farahmand, G. Bashiri, \textbf{Arash Abadpour}, ``\emph{Developing a system for cinematic measurement of body movements by imaging}'', In the 5th Iraninan Congress of Medical Physics (ICMP), Tehran, Iran,  2002, pp. 99-100 (Persian).}%W?
%\cvline{}{\textbf{Arash Abadpour}, ..., ``\emph{...}'', Submitted to ....}%W

\subsection{Dissertations}    

\cvline{}{\textbf{Ph.D. Thesis}: ``\emph{QoS-Constrained Information Theoretic Capacity Maximization in CDMA Systems}'', Electrical and Computer Engineering Department, University of Manitoba, Winnipeg, Manitoba, Canada,  Supervised by Prof. Attahiru Sule Alfa (Ph.D.), 2005--2009.}

\cvline{}{\textbf{M.Sc. Thesis}: ``\emph{Color Image Processing using Principal Component Analysis}'', Mathematics Science Department, Sharif University of Technology, Tehran, Iran, Supervised by Shohreh Kasaei (Ph.D.) and A. Daneshgar (Ph.D.), 2004--2005.}

\cvline{}{\textbf{B.Sc. Thesis}: ``\emph{Image Processing Integrated Debugging Environment}'', Electrical Engineering Department, Sharif University of Technology, Tehran, Iran, Supervised by Bijan Vosoughi Vahdat (Ph.D.), 2001--2002.}%

\subsection{Technical Reports}

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Jeff Diamond, ``\emph{Video Streaming using Overlay Networks}'', Technical Report, Telecommunication Research Laboratories (TRLabs), 2008.}%W289

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Jeff Diamond, ``\emph{Video-on-Demand Network Design And Maintenance Using Fuzzy Optimization}'', Technical Report, Telecommunication Research Laboratories (TRLabs), 2007.}%W261

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Anthony C.K. Soong, ``\emph{Capacity-Share Controlled Information-Theoretic Sum Capacity of Reverse Link Single-Cell CDMA Systems}'', Technical Report, University of Manitoba, 2006.}%W242

\cvline{}{\textbf{Arash Abadpour}, Attahiru Sule Alfa, and Anthony C.K. Soong, ``\emph{A More Realistic Approach to Information-Theoretic Sum Capacity of Reverse Link CDMA Systems in a Single Cell}'', Technical Report, University of Manitoba, 2006.}%W210

\cvline{}{A. Amirfazli, K. Khoshi, Azadeh Yadollahi, \textbf{Arash Abadpour},         ``\emph{Converting Industrial Drawings Type A to Type E from Non-Vector Form to Vector Form II}'', Research Proceedings, Sharif University of Technology, 2000--2001, pp. 31--39.}

\cvline{}{Roya Narimani, G. Bashiri, \textbf{Arash Abadpour}, ``\emph{Gait Analysis by Image Processing}'', Research Proceedings, Sharif University of Technology, 1999--2000, pp. 187--195.       }

\cvline{}{A. Amirfazli, K. Khoshi, Azadeh Yadollahi, \textbf{Arash Abadpour}, ``\emph{Converting Industrial Drawings Type A to Type E from Non-Vector Form to Vector Form I}'', Research Proceedings, Sharif University of Technology, 1999--2000, pp. 25--36.}

more: \href{https://scholar.google.com/citations?user=vWpVdeYAAAAJ}{Google Scholar}

full text: \href{http://abadpour.com}{abadpour.com}